A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Merge

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\parse}{\texttt{parse}\xspace}
\newcommand{\source}{\texttt{source}\xspace}
\newcommand{\substitute}{\texttt{substitute}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

@@

  \subsubsection{Metaprogramming} The combination of \eval and \substitute is
  used to do metaprogramming in R. \substitute can be used to synthesize ASTs by
  stitching together user inputs. \substitute walks over its argument AST and
  replaces the symbols with their bindings in the specified environment and
  returns this new AST which can then be evaluated in custom environments using
  \eval.

>>>>

\newcommand{\eval}{\texttt{eval}\xspace}
\newcommand{\substitute}{\texttt{substitute}\xspace}
\newcommand{\parse}{\texttt{parse}\xspace}
\newcommand{\source}{\texttt{source}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

@@

  \subsubsection{Metaprogramming} \eval in combination with \substitute is used
  to
  Assembling call strings from components passed by callers: eval(substitute(f(x, y, z)))
